Reasoning About a Machine with Local Capabilities

### 2019-03-06 toplas/paper.tex
minor

  We have made improvements to readability and completeness throughout the paper. For instance, we have added an introduction to \sectionname~\nameref{sec:logical-relation} that provides informal intuition about how the logical relation machinery comes into play on a capability machine. We highlight the following changes:

@@

  \item Proof sketches for the \nameref{thm:ftlr} and Lemma~\ref{lem:correctness-g1}, the correctness lemma for the awkward example.
  \item Figures that illustrate central parts of the calling convention.
  \item A section about malloc.

@@

  \item A section about macro instructions with descriptions of all the macros and the implementation of \texttt{scall}.
  \item A section on reasoning about programs that run on a capability machine.

@@

  \item Details previously found only in the technical appendix~\citep{technical_appendix} has been moved to the paper.
    Further, many of the details omitted in the paper has been added to the paper's appendix.

>>>>

  We have made improvements to readability and completeness throughout the paper.
  For instance, we have added an introduction to \sectionname~\nameref{sec:logical-relation} that provides informal intuition about how the logical relation machinery comes into play on a capability machine.
  We highlight the following changes:

@@

  \item We have added proof sketches for the \nameref{thm:ftlr} and for the correctness lemma for the awkward example
    (Lemma~\ref{lem:correctness-g1}).
  \item We have added figures that illustrate central parts of the calling convention.
  \item A section about malloc has been added.

@@

  \item A section about macro instructions with descriptions of all the macros and the implementation of \texttt{scall} has been added.
  \item We have added a section on reasoning about programs that run on a capability machine.

@@

  \item We have expanded on the explanation of the awkward example. 
  \item Details previously found only in the technical appendix~\citep{technical_appendix} have been moved to the paper.
